
The HACMS landshark system has been designed to prevent certain kinds of attacks. These are
listed in Section~\ref{sec:attack-protected}.  Some aspects of the system have not yet been
covered and are out of scope.
These are listed in Section~\ref{sec:attack-out-of-scope}. 

The red team will have access to the following to attempt to break into the Landshark or disrupt
communication.
\begin{enumerate}
  \item	Wireless radio communication between the Operator’s Control Unit (OCU) and the
    LandShark.
  \item	Full access to VM5, one of the 5 virtual machines running on the Black Box under
    Certikos including the USB ports on the front of the blackbox.
\end{enumerate}

\section{Protected components}
\label{sec:attack-protected}
This section lists the protected components of the system. 
\begin{enumerate}
  \item The communication between VM1 and the OCU has been secured using IPsec and Linux
    firewall.
    \begin{enumerate}
      \item This should prevent spoofing of the OCU or VM1 by attackers.
      \item This should prevent replay attacks.
    \end{enumerate}
  \item The communication between different VMs using the Kestrel stack using shared memory
    protected by Certikos.
  \item The system should be resilient to unplugging or spoofing one (and only one) of the following sensors
    \begin{enumerate}
      \item GPS
      \item Left side odometry
      \item Right side odometry
    \end{enumerate}
  %\item	Denial of Service (DoS) attacks over the radio?
  %\item	Denial of Service (DoS) attacks on a mailbox?
\end{enumerate}


\section{Unprotected components (out of scope)}
\label{sec:attack-out-of-scope}
The following things are not yet protected, so they are out of scope.
The red team may not attack the landshark system in the following ways.
\begin{enumerate}

  \item You may not modify the CF card except inside partition 13 (the Red Team VM).
  \item You may not read the IPSec private key stored in the partition 5 of the CF.
  \item	You may not attack the OCU. You may, however, try to spoof the IP packets from VM1 to the OCU.
  \item	You may not plug in any device in the back of the blackbox. 
  \item	You may not turn off power to the blackbox.
  \begin{enumerate}
    \item The firmware (specifically in the base controller) has not been protected. If the
      blackbox is powered off, it will keep moving (if it was moving at the time of the
      poweroff).
    \item This may corrupt the CF card.
  \end{enumerate}
\end{enumerate}

